|

### 2019-08-27 paper.Rmd
Trying to work out thickness required.

>>>>

The thickness of the slice should be chosen such that enough points are inside the slice be representative of the distribution. This will depend on the total number of points in the dataset, its original dimensionality and on the distribution. Here we estimate the number of points inside a slice of thickness $h$ for the rotation invariant example of an $n$ dimensional full hypersphere with radius $R$, assuming uniformly distributed points throughout the sphere. This means we calculate the relative volume inside the slice as a function of $h$ and $n$.

The total volume of the full hypersphere is given as
\begin{equation}
V_n(R) = \frac{\pi^{n/2}}{\Gamma(\frac{n}{2} + 1)} R^n.
\end{equation}
To calculate the volume of the slice we subtract the volume of a hypersphere cap of hight $h'=r-h$, as given in @capVol,
\begin{equation}
V^{\phi}_n(R) = \frac{1}{2}V_n(R) I_{sin^2\phi}(\frac{n+1}{2},\frac{1}{2}),
\end{equation}
where $I$ is the regularized incomplete beta function and $\phi =\arccos(1-\frac{h'}{r}) = \arccos(\frac{h}{r})$ the colatitude angle (XXX got this off the paper, don't yet understand the angle..).
The relative volume of the slice is thus given as (XXX better names needed!)
\begin{equation}
V_n^h(R) = \frac{V_n(R) - 2 V^{\phi}_n(R)}{V_n(R)} = 1 - I_{1-\frac{h^2}{r^2}}(\frac{n+1}{2},\frac{1}{2}),
\end{equation}
using $\sin(\arccos(x)) = \sqrt{1-x^2}$.

In the case of a hollow hypersphere we are instead interested in the relative area inside the slice. We use the cap area derived in @capVol to calculate the area inside the slice as
\begin{equation}
A_n^h(R) = \frac{A_n(R) - 2 A^{\phi}_n(R)}{A_n(R)} = 1 - I_{1-\frac{h^2}{r^2}}(\frac{n-1}{2},\frac{1}{2}).
\end{equation}

XXXX not sure this makes sense, need to check against plots (not what I was expecting, need to think about this more)
